Embedded Meta-Learning: Toward more flexible deep-learning models

### 2019-04-30 meta_RL_analyses.Rmd
Continuing figure + caption tuning

plot themes
```{r}
theme_set(theme_bw() + 
            theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()))
```

@@

ggsave("writing/figures/basic_meta_learning.png", width=5, height=3)
```

@@

#ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic_basic_random_meta.png", width=5, height=3.5)
ggsave("writing/figures/meta_mapping.png", width=5, height=3)
```

@@

```{r}
summary_plot(lang_meta_d %>%
               filter(epoch == 0,
                      meta_task %in% c("toggle_losers", "toggle_black_valuable"),
                      run_type %in% c("meta_batch_128", "language_simplified_random_holdout")),
             "named_meta_task", "reward", "is_new",
             other_baseline_data = meta_baseline_unmapped_d %>%
               filter(is_new == "Held out",
                      meta_task %in% c("toggle_losers", "toggle_black_valuable"))) +
  facet_wrap(. ~ named_run_type)  +
  guides(color=guide_legend(title=NULL)) +
  labs(x="Meta task", y="Average reward") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

#ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/language_meta.png", width=7, height=3.5)
ggsave("writing/figures/language_meta_mapping.png", width=5, height=3)

>>>>

plot themes
```{r}
theme_set(theme_bw() + 
            theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
                  legend.margin = margin(0, 0, 0, 0), 
                  legend.box.margin = margin(0, 0, 0, 0)))
```

@@

ggsave("writing/figures/basic_meta_learning.png", width=4.2, height=3)
```

@@

#ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic_basic_random_meta.png", width=5, height=3.5)
ggsave("writing/figures/meta_mapping.png", width=4.2, height=3)
```

@@

```{r}
summary_plot(lang_meta_d %>%
               filter(epoch == 0,
                      meta_task %in% c("toggle_losers", "toggle_black_valuable"),
                      run_type %in% c("meta_batch_128", "language_simplified_random_holdout")) %>%
               mutate(named_run_type = factor(named_run_type, labels=c("Random 50% holdout", "Targeted 10% holdout"))),

             "named_meta_task", "reward", "is_new",
             other_baseline_data = meta_baseline_unmapped_d %>%
               filter(is_new == "Held out",
                      meta_task %in% c("toggle_losers", "toggle_black_valuable"))) +
  facet_wrap(. ~ named_run_type)  +
  guides(color=guide_legend(title=NULL)) +
  labs(x="Meta task", y="Average reward") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

#ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/language_meta.png", width=7, height=3.5)
ggsave("writing/figures/language_meta_mapping.png", width=4.2, height=3)

### 2019-04-30 writing/embedded_meta_learning.tex
Continuing figure + caption tuning

\begin{figure}[H]

@@

\includegraphics[width=0.66\textwidth]{figures/basic_meta_learning.png}
\caption{Basic meta-learning successfully generalizes to held out tasks, both when trained on a random sample of half the tasks, or when a targeted subset is held out. The dashed line indicates chance performance, while the solid lines are optimal performance.}

@@

\includegraphics[width=0.66\textwidth]{figures/meta_mapping.png}
\caption{The system generalizes to meta-mapping new tasks. The system is trained to do the three meta-mappings shown here, and is able to generalize these mappings to tasks it has not been trained on. For example, for the ``losers'' mapping, the sytem is trained to map games to their losers variants. When given a game it has not mapped in this way, it is able to map it to the losers variation. This plot shows the reward produced by taking the mapped embedding and playing the targeted game.}

@@

\textbf{Basic language (language $\rightarrow$ task):} Next, we show that the system is able to perform a held-out task based on a linguistic description alone. The system is significantly better than chance at this task, as shown in Fig. \ref{cards_language_basic_results}, but it is substantially less successful at this task than at learning from examples. This is perhaps unsurprising, however, since examples contain richer information about the structure of the task. (Note that the targeted 10\% was run using an older version of the code. Results may improve slightly when it is re-run, but based on the random 50\% hold-out results, the change doesn't make too substantial a difference.)\par
Intriguingly, the system also shows more run-to-run variability in its generalization from language, especially with a targeted hold-out. This suggests that language learning in this context may be quite sensitive to initialization, possibily because of the poverty of the signal relative to the capacity of the network. Interestingly, simply applying dropout does not seem to ameliorate this. \par
\begin{figure}[H]
\begin{subfigure}[t]{0.5\textwidth}
\includegraphics[width=\textwidth]{figures/language_basic.png}
\caption{Average rewards}
\begin{subfigure}[t]{0.5\textwidth}
\includegraphics[width=\textwidth]{figures/language_basic_by_run.png}
\caption{Density plot of rewards received on different held-out tasks on different runs of the model.}
\caption{The system generalizes to held out tasks based on language alone. However, it is substantially less good at this task than generalizing to a held-out task based on examples. Furthermore, it shows more run-to-run variability and within-run variability.}
\label{cards_language_basic_results}
\textbf{Meta language (language $\rightarrow (\text{task} \rightarrow \text{task})$):} Finally, in Fig, \ref{cards_language_meta_results}, we show that the system is able to perform meta-mappings from language comparably to how it performs them from examples. Note that this is in some ways an easier task than the basic language-mapping task. \par
\begin{figure}[H]
\includegraphics[width=0.66\textwidth]{figures/language_meta_mapping.png}
\caption{The system generalizes to meta-mapping new tasks based on language. It performs this comparably to meta-mapping based on examples of mappings.}
\label{cards_language_meta_results}

@@

>>>>

\begin{figure}

@@

\includegraphics[width=0.5\textwidth]{figures/basic_meta_learning.png}
\caption{Basic meta-learning successfully generalizes to held out tasks, both when trained on a random sample of half the tasks, or when a targeted subset is held out. The gray dashed line indicates chance performance, while the solid lines are optimal performance. The colored dashed lines show how well the system could perform by playing the strategy from the most correlated game it has seen. The fact that it generally exceeds this difficult baseline shows a deeper form of generalization than just memorizing a few strategies and picking the closest one.}

@@

\begin{subfigure}{0.5\textwidth}
\includegraphics[width=\textwidth]{figures/meta_mapping.png}
\caption{From examples of mapping.}
\label{cards_meta_map_results_examples}
\begin{subfigure}{0.5\textwidth}
\includegraphics[width=\textwidth]{figures/language_meta_mapping.png}
\caption{From language input.}
\label{cards_meta_map_results_language}
\caption{The system generalizes to meta-mapping new tasks. The system is trained to do the meta-mappings shown here on a subset of its basic tasks, and is able to generalize these mappings to novel tasks it has not been trained on. For example, for the ``losers'' mapping, the sytem is trained to map games to their losers variants. When given a novel game, it is able to apply this mapping to guess how to play the losers variation. This plot shows the reward produced by taking the mapped embedding and playing the targeted game. The gray dashed line indicates random performance, while the colored dashed lines indicate performance if the system did not alter its behavior in response to the meta-mapping. The system generally exceeds these baselines by a wide margin, although the switch-suits baseline is more difficult with the targeted holdout. Furthermore, the system is able to execute these mappings either from examples (\subref{cards_meta_map_results_examples}) or from language cues (\subref{cards_meta_map_results_language}).}

@@

%\textbf{Basic language (language $\rightarrow$ task):} Next, we show that the system is able to perform a held-out task based on a linguistic description alone. The system is significantly better than chance at this task, as shown in Fig. \ref{cards_language_basic_results}, but it is substantially less successful at this task than at learning from examples. This is perhaps unsurprising, however, since examples contain richer information about the structure of the task. (Note that the targeted 10\% was run using an older version of the code. Results may improve slightly when it is re-run, but based on the random 50\% hold-out results, the change doesn't make too substantial a difference.)\par
%Intriguingly, the system also shows more run-to-run variability in its generalization from language, especially with a targeted hold-out. This suggests that language learning in this context may be quite sensitive to initialization, possibily because of the poverty of the signal relative to the capacity of the network. Interestingly, simply applying dropout does not seem to ameliorate this. \par
%\begin{figure}[H]
%\begin{subfigure}[t]{0.5\textwidth}
%\centering
%\includegraphics[width=\textwidth]{figures/language_basic.png}
%\caption{Average rewards}
%\end{subfigure}%
%\begin{subfigure}[t]{0.5\textwidth}
%\includegraphics[width=\textwidth]{figures/language_basic_by_run.png}
%\caption{Density plot of rewards received on different held-out tasks on different runs of the model.}
%\end{subfigure}
%\caption{The system generalizes to held out tasks based on language alone. However, it is substantially less good at this task than generalizing to a held-out task based on examples. Furthermore, it shows more run-to-run variability and within-run variability.}
%\label{cards_language_basic_results}
%\end{figure}
%\newpage
%\textbf{Meta language (language $\rightarrow (\text{task} \rightarrow \text{task})$):} Finally, in Fig, \ref{cards_language_meta_results}, we show that the system is able to perform meta-mappings from language comparably to how it performs them from examples. Note that this is in some ways an easier task than the basic language-mapping task. \par
%\begin{figure}[H]
%\centering
%\includegraphics[width=0.66\textwidth]{figures/language_meta_mapping.png}
%\caption{The system generalizes to meta-mapping new tasks based on language. It performs this comparably to meta-mapping based on examples of mappings.}
%\label{cards_language_meta_results}
%\end{figure}

@@

\newpage
\appendix

\section{Detailed methods}
\subsection{Datasets}
\subsubsection{Polynomials}

\subsubsection{Card games}
